Cosmological constraints from the redshift dependence of the galaxy angular 2-point correlation function

### 2016-08-26 draft/draft0.tex
updates

The HR4 simulation  \citep{hr4} used a box size $L={3150}$ $h^{-1}$Mpc, 
and $N=6300^3$ particles.  
The simulation used the second order Lagrangian perturbation theory (2LPT) initial conditions at $z_{i}=100$ and a WMAP5 cosmology
$(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96) \citep[]{komatsu 2011}, 
yielding a particle mass of $m_{p} \simeq 9.02 \times 10^9 \hMsun$.
This starting redshift, combined  with 2LPT initial conditions, ensures an accurate mass function and power spectrum \citep{2014NewA...30...79L}.

Mock galaxy samples are produced from the HR4 simulation by using a modified version of the one-to-one correspondence scheme \citep{hong2016}. 
The most bound member particles (MBPs) of simulated halos are adopted as the tracer of galaxies rather than the subhalos,
and the merger timescale is taken into account in the lifetime of merged halos.
We built the merger trees of simulated halos by tracking their MBPs from $z = 12$ to 0.
When a merger event occurs, we calculate the merger timescale described in \cite{jiang2008} (hereafter J08)
to determine when a satellite galaxy is completely disrupted.
%We modeled the position and the velocity of a galaxy from the position and velocity of its corresponding MBP.
By using the abundance matching, 
we modeled the luminosity of a central/isolated galaxies from their current mass
and of satellite galaxies 
from their mass at the time of infall.

\cite{hong2016} compared the 2pCF of our mock galaxy sample at $z = 0$ to the SDSS DR7 volume-limited galaxy sample \citep{zehavi2011}.
%When a typical subhalo-galaxy correspondence scheme is applied, 
%the 2pCF from our simulation is smaller than the observation and does not show a proper Finger-of-God (FOG) feature in our simulation resolution. 
%We found that %the %2pCF of our galaxy sample agrees well with the observation.
The simulated 2pCF shows a similar finger of god (FOG) feature \citep{FOG} as the observation in the contour map, 
and the projected 2pCF agrees with the observation within 1$\sigma$ deviation on scales greater than 1 ${h^{-1}}$Mpc.

%As will be introduced in the next section, 
The HR4 simulation yield one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc.
As shown in \cite{bossAP},
from one all-sky survey, 
we are able to create four sets of non-overlapping north Galactic cap (NGC) samples for CMASS and LOWZ, 
or eight sets of non-overlapping south Galactic cap (SGC) samples.
In this paper we use these simulated galaxies for the estimation of the systematics in the 2pCF of the observed galaxies.

@@

We measure the 2pCF in redshift bins of galaxies and 
determine cosmological parameters by examining the redshift evolution of clustering anisotropy.
Mock survey samples are used to correct the results for the systematics and to estimate the covariance.
%Our procedure is as follows.

>>>>

We test the method on the Horizon Run 4  (HR4) simulation \citep{hr4}.
HR4 used $N=6300^3$ particles in a box size of $L={3150}$ $h^{-1}$Mpc.  
It adopted the second order Lagrangian perturbation theory (2LPT) initial conditions at $z_{i}=100$
and a WMAP5 cosmology $(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96) \citep[]{komatsu 2011}.
The particle mass is $\simeq m_{p} \simeq 9.02 \times 10^9 \hMsun$.
%This starting redshift, combined  with 2LPT initial conditions, ensures an accurate mass function and power spectrum \citep{2014NewA...30...79L}.

Mock galaxy samples are produced from the simulation based on a modified one-to-one correspondence scheme \citep{hong2016}. 
The most bound member particles (MBPs) of simulated halos are adopted as the tracer of galaxies,
and the merger timescale is computed to get the lifetime of merged halos.
Merger trees of simulated halos are constructed by tracking their MBPs from $z = 12$ to 0.
When a merger event occurs, we adopt the formular of \cite{jiang2008} to calculate the merger timescale 
and determine when a satellite galaxy is completely disrupted.
%We modeled the position and the velocity of a galaxy from the position and velocity of its corresponding MBP.
%By using the abundance matching, 
%we modeled the luminosity of a central/isolated galaxies from their current mass
%and of satellite galaxies from their mass at the time of infall.

\cite{hong2016} compared the 2pCF of the SDSS DR7 volume-limited galaxy sample \citep{zehavi2011} and the HR4 $z=0$ mock galaxies.
%When a typical subhalo-galaxy correspondence scheme is applied, 
%the 2pCF from our simulation is smaller than the observation and does not show a proper Finger-of-God (FOG) feature in our simulation resolution. 
%We found that %the %2pCF of our galaxy sample agrees well with the observation.
The mock galaxies shows a similar finger of god (FOG) feature \citep{FOG} as the observation.
On scales greater than 1 ${h^{-1}}$Mpc., 
the projected 2pCF of the mock and observational samples agree within 1$\sigma$ deviation.

%As will be introduced in the next section, 
The output of HR4 simulation includes one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc 
and a series ({\bf how many?}) of snapshot mock galaxy catalogues at different redshifts.
In this paper we use five snapshot data at $z=0,0.5,1,1.5,2$.
We require subhalos to have at least 30 member particles, 
so the minimal mass of galaxies is $\simeq m_{p} \simeq 2.7 \times 10^{11} \hMsun$.
At the five redshifts, we get a number of
%$4.57\times 10^8$, $4.06\times 10^8$, $3.52\times 10^8$, $3.06\times 10^8$ and $2.28 \times 10^8$ mock galaxies,
457, 406, 352, 206 and 228 million mock galaxies,
corresponding to a number density of 
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
1.46, 1.30, 1.13, 0.98 and 0.73 in unit of $ 10^{-2} h^{3} \rm Mpc^{-3}$,
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
respectively.

@@

We measure the angular 2pCF in the five redshifts.
We determine cosmological parameters by examining the redshift evolution of clustering anisotropy.
Mock survey samples are used to correct the results for the systematics and to estimate the covariance.
%Our procedure is as follows.
